---
name: Louis
surname: Lippens
position: Postdoctoral Researcher
qualifications: MSc, MM, PhD
address: Ghent University (FEB), Sint-Pietersplein 6, 9000 Gent, Belgium
profilepic: Louis_Anneke_sq_bw.jpg
www: louislippens.be
email: Louis.Lippens@UGent.be
github: lglip
linkedin: louislippens
researchgate: Louis-Lippens
date: "`r format(Sys.time(), '%b %Y')`"
headcolor: "333333"
docname: Resume
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multirow}
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

'%!in%' <- function(x,y)!('%in%'(x,y))
Sys.setlocale("LC_ALL","English")

library(vitae)
library(tidyverse)
library(knitr)
library(kableExtra)
library(scholar)
```

# About Me

\footnotesize
I am a **postdoctoral researcher** in **labour economics** at Ghent University. My academic work focuses on what determines and solves labour market discrimination. My **postdoctoral project** delves into the relationship between **competition** and **discrimination**. More broadly, as an affiliated researcher at **UGent @ Work**, I collaborate on **interdisciplinary projects** addressing key challenges in the **labour market**, translating research results into **evidence-based policy advice**. I hold a **master’s degree** in **work psychology** from Ghent University and a business degree in **general management** from Vlerick Business School. Prior to re-entering academia and obtaining a **joint PhD in economics and sociology** from Ghent University and Free University Brussels, I worked in management consulting, where I gained experience in data governance and data analytics.
\normalsize

```{r}
brief <- tribble(
  ~what, ~when, ~with,
  "what", "when", "with"
)

detail <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "what", "when", "with", "where", "why"
)

#brief %>% brief_entries(what = what, when = when, with = with)
#detail %>% detailed_entries(what = what, when = when, with = with, where = where, why = why)
```

# Employment

\medskip
## Academia (Full-time)
```{r academia}
academia <- tribble(
  ~position, ~period, ~organisation, ~location, ~description,
  
  "Postdoctoral Researcher", "Oct. 2023 -- Present", "Ghent University", "Ghent, BE",
  list("FWO postdoctoral fellowship project on how market competition can diminish labour market discrimination,  using advanced statistical techniques such as multilevel meta-regression on transnational data",
       "Co-lecturer Labour Economics course"),
  
  "Affiliated Researcher", "Jun. 2021 -- Present", "UGent @ Work", "Ghent, BE",
  list("Research on topics in labour economics, contributing to solving economic and societal questions surrounding the (Belgian) labour market",
       "Translation of labour market research into evidence-based policy advice"),
  
  "Doctoral Researcher", "Aug. 2019 -- Sep. 2023", "Ghent University", "Ghent, BE",
  list("Teaching assignments, such as guiding last-year students with their master's thesis, coaching bachelor students on migration research topics, and giving guest lectures on empirical/experimental economic research",
       "Development of low-threshold, interactive, and flexible tools (e.g. multicultural situational judgment tests) to increase the awareness of HR professionals' intercultural competence and to empower them to deal with the drivers of their competence",
       "Dissertation on (ethnic) hiring discrimination, its determinants, its mechanisms, and the influence of the organisational context"),
  
  "Visiting Doctoral Researcher", "Aug. 2019 -- Jul. 2023", "Free University Brussels", "Brussels, BE",
  "Research on topics in sociology of labour",
)

academia %>%
  detailed_entries(
    what = position,
    when = period,
    with = organisation,
    where = location,
    why = description
  )
```

\medskip
## Private Sector (Full-time)
```{r private sector}
privatesector <- tribble(
  ~position, ~period, ~organisation, ~location, ~description,
  
  "Senior Consultant (Data Analytics)", "Oct. 2018 -- Jul. 2019", "BDO", "Flanders region, BE",
  list("Performed survey research on the modal shift in transportation and developed a predictive model for a governmental body and an inland port",
       "Advised a private company active in the entertainment industry on the design of a data asset repository",
       "Constructed a financial model for a mid-scale mobility management project"),
  
  "Consultant (Data Governance)", "Sep. 2017 -- Sep. 2018", "Capgemini Invent", "Brussels, BE",
  list("Performed a benchmark study of data governance operating models in financial services",
       "Developed and optimised various data asset documentation processes in the context of BCBS239 and GDPR regulatory frameworks",
       "Conducted a data quality maturity assessment across various business and functional departments within a major Belgian bank",
       "Set up data-sharing agreements between various business and functional departments within a major Belgian bank")
)

privatesector %>%
  detailed_entries(
    what = position,
    when = period,
    with = organisation,
    where = location,
    why = description
  )
```

```{r internships}
#latex
# \medskip
# ## Internships (Full-time)

internships <- tribble(
  ~position, ~period, ~organisation, ~location, ~description,
  
  "Management Consultant", "May 2017 -- Jun. 2017", "CEMAC", "Ghent, BE",
  list("Redesign of the firm's organisational structure and internal business processes",
       "Analysis of the firm's product strategy and internationalisation opportunities and capabilities"),
  
  "HR Consultant", "Sep. 2015 -- Jan. 2016", "The Future Alliance", "Ghent, BE",
  list("Organised assessment and development centres for middle management candidates",
       "Organised workshops concerning HR-related topics (e.g. giving and receiving feedback)",
       "Carried out recruitment and selection assignments for entry and (middle) management functions"),
  
  "HR Consultant", "Oct. 2014 -- Nov. 2014", "Hudson", "Ghent, BE",
  list("Developed 40 rating scales, including a manual, for the advisory firm's dedicated competency model")
)

stop <-
  internships %>%
  detailed_entries(
    what = position,
    when = period,
    with = organisation,
    where = location,
    why = description
  )
```

\medskip
## Social Sector (Part-time)
```{r social sector}
socialsector <- tribble(
  ~position, ~period, ~organisation, ~location, ~description,
  
  "Human Capital Director", "Jul. 2015 -- Jun. 2016", "180 Degrees Consulting (180DC)", "Ghent, BE",
  list("180DC is the world's largest international consultancy for non-profits and social enterprises",
       "Led the human capital activities of 180DC's Ghent University branch",
       "Conducted selection tests, incl. reasoning tests and structured interviews, of about 70 university students",
       "Other activities: implementation of 180° feedback system, social media marketing, event support"),
  
  "Management Consultant", "Mar. 2015 -- Jun. 2015", "180 Degrees Consulting", "Ghent, BE",
  list("Co-developed an integrated fundraising and marketing strategy for the NGO Join For Water",
       "Conducted survey research regarding the brand perceptions of Join For Water's donors and sympathizers",
       "Developed an evidence-based, bespoke brand personality for Join For Water, as well as brand improvement guidelines")
)

socialsector %>%
  detailed_entries(
    what = position,
    when = period,
    with = organisation,
    where = location,
    why = description
  )
```

# Education
```{r education}
education <- tribble(
  ~degree, ~period, ~institution, ~location, ~description,
  
  "PhD, Economics", "Aug. 2019 -- Aug. 2023", "Ghent University", "Ghent, BE",
  list("Doctoral courses: Advanced Econometrics (Non-Linear Techniques), Advanced Labour Economics, Multilevel Analysis",
       "Other courses: Econometrics, Labour Economics, Advanced Academic Writing in English, Multilevel Analysis in R, Generalised Linear Models in R, Multidisciplinary Research Tools to Study Work and the Labour Market, Effective Graphical Displays",
       "Supervisors: Prof. Stijn Baert, Prof. Eva Derous"),
  
  "PhD, Sociology", "Aug. 2019 -- Aug. 2023", "Free University Brussels", "Brussels, BE",
  list("Supervisor: Prof. Pieter-Paul Verhaeghe (Joint PhD with UGent as the main institution)"),
  
  "MM, General Management (Magna Cum Laude)", "Sep. 2016 -- Jun. 2017", "Vlerick Business School", "Ghent, BE",
  list("Key Courses: Corporate Finance, Financial Accounting, Management Accounting and Control, Strategic Management, Operations Management",
       "Electives: Big Data and Data Analytics, Digital Strategy (w/ BNPP Fortis), Strategy and Organisational Design, Mergers and Acquisitions (w/ Gimv)",
       "Bootcamp: Strategic Innovation in Renewable Energy (w/ Durabilis)"),
  
  "MSc, Industrial and Organisational Psychology (Magna Cum Laude)", "Sep. 2011 -- Jun. 2016", "Ghent University", "Ghent, BE",
  list("Key Courses: Multi-level Organisational Research, Statistics, Applied Data Analysis, Human Resource Management, Industrial Relations",
       "Master's thesis: Short form of the Wilde Intelligenztest: Psychometric qualities and utility of a 12-minute intelligence test for personnel selection")
)

education %>%
  detailed_entries(
    what = degree,
    when = period,
    with = institution,
    where = location,
    why = description
  )
```

# Publications
```{r pubs}
profile_id <- "N5hW-KgAAAAJ"
citations <- get_profile(profile_id)
publications <- get_publications(profile_id, flush = TRUE, sortby = "year") %>%
  select(title, author, journal, cites, year) %>%
  arrange(desc(year), journal)
```

\medskip
## Peer-reviewed Publications
```{r pr pubs}
exception <-
  c("Is labour market discrimination against ethnic minorities better explained by taste or statistics? A systematic review of the empirical evidence")

publications %>%
  filter(!str_detect(journal, c("IZA Discussion Paper|arXiv|Ghent University|Stories @ UGent @ Work|In conflict gaan met je baas")),
         title != "Discriminatie") %>%
  slice(1:3) %>%
  mutate(rows = case_when(title %in% exception ~ 3.55,
                          TRUE ~ 2.75)) %>%
  brief_entries(what = glue::glue("\\textbf{<journal>} \\newline <title> \\newline <author>",
                                  .open = "<", .close = ">"),
                when = glue::glue("\\multirow{-<rows>}{=}{<year>}",
                                  .open = "<", .close = ">"),
                .protect = FALSE)

publications %>%
  filter(!str_detect(journal, c("IZA Discussion Paper|arXiv|Ghent University|Stories @ UGent @ Work|In conflict gaan met je baas")),
         title != "Discriminatie") %>%
  slice(4:7) %>%
  mutate(rows = case_when(title %in% exception ~ 3.55,
                          TRUE ~ 2.75)) %>%
  brief_entries(what = glue::glue("\\textbf{<journal>} \\newline <title> \\newline <author>",
                                  .open = "<", .close = ">"),
                when = glue::glue("\\multirow{-<rows>}{=}{<year>}",
                                  .open = "<", .close = ">"),
                .protect = FALSE)
```

\medskip
## Discussion Papers
```{r disc pubs}
exception <-
  c("An Arab, an Asian, and a Black guy walk into a job interview: ethnic stigma in hiring after controlling for social class")

publications %>%
  filter(str_detect(journal, c("IZA Discussion Paper|arXiv"))) %>%
  mutate(journal = case_when(str_detect(journal, "IZA") ~ "IZA Institute of Labour Economics",
                             str_detect(journal, "arXiv") ~ "arXiv"),
         rows = case_when(title %in% exception ~ 3.55,
                          TRUE ~ 2.75)) %>%
  brief_entries(what = glue::glue("\\textbf{<journal>} \\newline <title> \\newline <author>",
                                  .open = "<", .close = ">"),
                when = glue::glue("\\multirow{-<rows>}{=}{<year>}",
                                  .open = "<", .close = ">"),
                .protect = FALSE)
```

```{r conf pubs}
#\medskip
## Conference Papers
wp <- tribble(
  ~journal, ~title, ~author, ~year,
  "17th Belgian Day for Labour Economists", "Understanding ethnic hiring discrimination: A contextual analysis of experimental evidence", "L Lippens, A Dalle, F D'hondt, PP Verhaeghe, S Baert", "2022"
)

stop <- wp %>%
  as.data.frame() %>%
  brief_entries(what = glue::glue("\\textbf{<journal>} \\newline <title> \\newline <author>",
                                  .open = "<", .close = ">"),
                when = glue::glue("\\multirow{-2.75}{=}{<year>}",
                                  .open = "<", .close = ">"),
                .protect = FALSE)
```

\scriptsize
Visit my Google Scholar profile at https://bit.ly/louis-lippens-scholar for a comprehensive overview of my research.
\normalsize

# Services and Outreach

\medskip
## Peer Review
\footnotesize
In addition to conducting my own research, I have also reviewed the work of some of my peers. I have served as a reviewer (ad hoc) for **American Sociological Review** (1), **Journal of Labor Economics** (1), **Technology in Society** (1), **Journal of Ethnic and Migration Studies** (1), **Social Science & Medicine** (1), **Social Forces** (1), **PLOS ONE** (2), **Journal of Sociology** (1), **Work and Occupations** (1), **Social Policy and Society** (1), **International Migration Review** (1), **The Annals of Regional Science** (1), **Oxford Bulletin of Economics and Statistics** (1), **International Journal of Manpower** (1), and **Economics Bulletin** (2).
\normalsize

\medskip
## Academic Outreach
```{r academic outreach}
outreach_a <- tribble(
  ~conference, ~year, ~location, ~topic,
  "Artificial Intelligence and The Economy", "2023", "Berlin, DE",
  "Computer says 'no': Exploring systemic hiring bias in ChatGPT using an audit approach",
  
  "Belgian Day for Labour Economists", "2022", "Brussels, BE",
  "Understanding ethnic hiring discrimination: A contextual analysis of experimental evidence",
  
  "CESSMIR Conference", "2022", "Ghent, BE",
  "Understanding ethnic hiring discrimination: A contextual analysis of empirical evidence",
  
  "IMISCOE Annual Conference", "2022", "Oslo, NO",
  "The state of hiring discrimination: A meta-analysis of (almost) all recent correspondence experiments",
  
  "Spring Meeting of Young Economists", "2022", "Orléans, FR",
  "The state of hiring discrimination: A meta-analysis of (almost) all recent correspondence experiments",
  
  "CESSMIR Conference", "2021", "Ghent, BE",
  "The state of hiring discrimination: A meta-analysis of (almost) all recent correspondence experiments",
  
  "EALE Annual Conference", "2021", "Barcelona, ES \\newline (online)",
  "Is labour market discrimination against ethnic minorities better explained by taste or statistics?",
  
  "Day of Sociology", "2021", "Utrecht, NL \\newline (online)",
  "Taste-based discrimination: Actually a matter of contact avoidance?",
  
  "CESSMIR Research Day", "2021", "Ghent, BE",
  "Taste-based discrimination: Actually a matter of contact avoidance?",
  
  "Faculty of Economics and Business Administration Research Day", "2021", "Ghent, BE",
  "Loss aversion in taste-based employee discrimination: Evidence from a choice experiment",
  
  "Context Matters Symposium", "2020", "Brussels, BE",
  "Is labour market discrimination against ethnic minorities better explained by taste or statistics?"
)

outreach_a %>%
  brief_entries(
    what = glue::glue("\\textbf{<conference>} \\newline <topic>",
                      .open = "<", .close = ">"),
    when = glue::glue("\\multirow{-1.9}{=}{<year>}",
                      .open = "<", .close = ">"),
    with = glue::glue("<location>",
                      .open = "<", .close = ">"),
    .protect = FALSE
  )
```

\newpage
## Societal Outreach
```{r societal outreach}
outreach_s <- tribble(
  ~outlet, ~type, ~year, ~audience, ~topic, ~rows,
  "VRT NWS", "News broadcast", "2023", "Belgian population",
  "Onderzoek discriminatie arbeidsmarkt", 1.9,
  
  "De Standaard", "Newspaper article", "2023", "Belgian population",
  "Oud is out, vooral op de Europese werkvloer", 1.9,
  
  "Radio 1", "Radio interview", "2023", "Belgian population",
  "Nog altijd discriminatie rond leeftijd en afkomst op arbeidsmarkt", 1.9,
  
  "Het Nieuwsblad; Gazet van Antwerpen", "Newspaper article", "2023", "Belgian population",
  "Oud is out, vooral in Europa", 1.9,
  
  "Het Belang van Limburg", "Newspaper article", "2023", "Belgian population",
  "Bedrijven discrimineren meer op leeftijd en looks dan op etniciteit", 1.9,
  
  "De Morgen", "Newspaper article", "2023", "Belgian population",
  "Wie jong en knap is, heeft de grootste kansen op de arbeidsmarkt", 1.9,
  
  "Het Laatste Nieuws", "Newspaper article", "2023", "Belgian population",
  "Hoe knapper je bent, hoe meer kans op een job", 1.9,
  
  "Le Soir", "Newspaper article", "2023", "Belgian population",
  "L'âge, le physique et le handicap, premier facteurs de discrimination à l'embauche", 1.9,
  
  "UGent @ Work", "Blog post", "2022", "Belgian population",
  "Measuring intentions to discriminate: in writing, open and exposed", 1.9,
  
  "UGent @ Work", "Blog post", "2022", "Belgian population",
  "Ethnic labour market discrimination: Generalisation or aversion?", 1.9,
  
  "HR Magazine", "Magazine article", "2022", "HR professionals",
  "The structured interview best predicts a good match", 1.9,
  
  "LinkedIn", "Blog post", "2022", "HR professionals",
  "The top-ranked selection tools to hire the best-performing candidate", 1.9,
  
  "Het Laatste Nieuws", "Newspaper article", "2021", "Belgian population",
  "Oudere sollicitanten krijgen bijna 50 procent minder positieve reacties", 1.9,
  
  "Trends (magazine)", "Newspaper article", "2021", "Belgian population",
  "Leeftijdsdiscriminatie op arbeidsmarkt is erger dan etnische discriminatie", 1.9,
  
  "UGent @ Work", "Blog post", "2021", "Belgian population",
  "Does discrimination have a price?", 1.9,
  
  "Radio 1, Nieuwe Feiten", "Radio interview", "2021", "Belgian population",
  "Loonopslag of liever werken met alleen autochtone Vlamingen?", 1.9,
  
  "Apache", "Newspaper article", "2020", "Belgian population",
  "Trainingen tegen arbeidsmarktdiscriminatie", 1.9,
  
  "Het Laatste Nieuws", "Newspaper article", "2020", "Belgian population",
  "Mijn job verdwijnt, mijn loon wordt kleiner, mijn promotie wordt gefnuikt: Dit is hoe de Vlamingen denken over de toekomst van hun werk", 2.9
)

outreach_s %>%
  slice(1:16) %>%
  brief_entries(
    what = glue::glue("\\textbf{<outlet>} \\newline <topic>",
                      .open = "<", .close = ">"),
    when = glue::glue("\\multirow{-<rows>}{=}{<year>}",
                      .open = "<", .close = ">"),
    with = glue::glue("<type>",
                      .open = "<", .close = ">"),
    .protect = FALSE
  )

outreach_s %>%
  slice(17:18) %>%
  brief_entries(
    what = glue::glue("\\textbf{<outlet>} \\newline <topic>",
                      .open = "<", .close = ">"),
    when = glue::glue("\\multirow{-<rows>}{=}{<year>}",
                      .open = "<", .close = ">"),
    with = glue::glue("<type>",
                      .open = "<", .close = ">"),
    .protect = FALSE
  )
```

# Skills

\medskip
## General Skills
```{r general, results = 'markup'}
general <- tribble(
  ~Research, ~Analytics, ~Business,
  "Audit studies -- Survey research -- Experimental research -- Applied psychometrics",
  "(Ordered) logit models -- Linear models -- Meta-analysis -- Meta-regression -- Reliability and validity analysis -- Structural equation modeling",
  "Project management -- Human capital management -- Corporate finance -- Advisory"
)

general %>%
  kable(booktabs = TRUE, align = 'c', escape = FALSE, format = "latex") %>%
  kable_styling(full_width = FALSE, font_size = 9, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = TRUE, color = "#5d5d5d") %>%
  row_spec(1, bold = FALSE, color = "#5d5d5d") %>%
  column_spec(column = 1:3, width = "5.2cm")
```

## Technical Skills
```{r technical, results = 'markup'}
technical <- tribble(
  ~`Coding Languages`, ~`Research Software`, ~`Business Software`, ~`Creative Software`, ~Other,
  "R (ggplot2, tidyverse, hugo, xaringan, quarto...) -- SQL",
  "RStudio -- Stata -- SPSS -- Knime",
  "Collibra -- MS Office",
  "Photoshop -- GIMP -- Ableton Live",
  "Git -- Markdown -- LaTeX"
)

technical %>%
  kable(booktabs = TRUE, align = 'c', escape = FALSE, format = "latex") %>%
  kable_styling(full_width = FALSE, font_size = 9, latex_options = "HOLD_position") %>% 
  row_spec(0, bold = TRUE, color = "#5d5d5d") %>%
  row_spec(1, bold = FALSE, color = "#5d5d5d") %>%
  column_spec(column = 1:5, width = "2.96cm")
```

## Languages
```{r languages, results = 'markup'}
languages <- tribble(
  ~Skill, ~Dutch, ~English, ~French,
  "Reading", "C2", "C2", "C1",
  "Writing", "C2", "C2", "B1",
  "Listening", "C2", "C2", "B2",
  "Speaking", "C2", "C1", "B1",
)

languages %>%
  kable(booktabs = TRUE, align = 'c', escape = FALSE, format = "latex") %>%
  kable_styling(full_width = FALSE, font_size = 9, latex_options = "HOLD_position") %>%
  footnote(
    footnote_as_chunk = TRUE,
    general_title = " ",
    general = "\\\\tiny \\\\textcolor[HTML]{5D5D5D}{Note. CEFR: A1/A2: Basic User; B1/B2: Independent User; C1/C2: Proficient User.}",
    escape = FALSE
  ) %>%
  row_spec(0, bold = TRUE, color = "#5d5d5d") %>%
  row_spec(1:4, bold = FALSE, color = "#5d5d5d") %>%
  column_spec(column = 1, bold = TRUE) %>%
  column_spec(column = 1:4, width = "2cm")

#credits for this code chunk: https://github.com/loreabad6/
```

```{r certificates}
certificates <- tribble(
  ~certificate, ~year, ~institution, ~affiliation,
  "Exploratory Data Analysis", "2019", "Coursera", "Johns Hopkins University",
  "Reproducible Research", "2018", "Coursera", "Johns Hopkins University",
  "R Programming", "2019", "Coursera", "Johns Hopkins University",
  "Financial Markets", "2017", "Coursera", "Yale University",
  "Fundamentals of Quantitative Modeling", "2017", "Coursera", "Wharton School",
  "Collibra Community Manager", "2017", "Collibra", "",
  "Collibra Data Steward", "2017", "Collibra", ""
)

#certificates %>%
#brief_entries(
#what = glue::glue("\\textbf{<certificate>} (<affiliation>)",
#                 .open = "<", .close = ">"),
#when = glue::glue("\\multirow{-.94}{=}{<year>}",
#                  .open = "<", .close = ">"),
#with = institution,
#.protect = FALSE
#)
```

# Honors, Grants, and Awards
\medskip
```{r awards}
awards <- tribble(
  ~award, ~year, ~institution, ~description, ~rows,
  "FWO Junior Postdoctoral Fellowship", "2023", "FWO Research Foundation -- Flanders",
  "Following (international) peer review of my postdoctoral project on competition and discrimination, I was awarded a three-year postdoctoral fellowship starting October 2023 (award rate: 21.2\\%).", 3,
  
  "Student Achievement for Outstanding Performance", "2017", "Vlerick Business School",
  "Personal recognition for obtaining the most and highest positive peer evaluations in group assignments throughout the academic year.", 3,
  
  "Best European Consulting Branch", "2015", "180 Degrees Consulting",
  "180 Degrees Consulting Ghent was named the best overall European branch (Europe) of the world's largest consultancy for non-profits and social enterprises. We were lauded for our collaboration-fostering spirit, high client focus and professional approach to private partnerships.", 4,
  
  "Best Event of Brugge", "2012 -- \\newline 2015", "Villa Bota",
  "During my time as event manager of an organisation active in entertainment, we won three 'Best of Brugge'; more than 3000 people casted their online vote for the 2015 edition.", 3
)

awards %>%
  filter(award != "Best Event of Brugge") %>%
  brief_entries(
    what = glue::glue("\\textbf{<award>} \\newline <description>",
                      .open = "<", .close = ">"),
    when = glue::glue("\\multirow{-<rows>}{=}{<year>}",
                      .open = "<", .close = ">"),
    with = institution,
    .protect = FALSE
  )
```

